\section{Introduction and Motivation}
The escalating housing costs in contemporary real estate markets have created significant barriers for first-time homebuyers. This demographic often faces the daunting task of accumulating substantial down payments amidst economic volatility and uncertain income trajectories. This research addresses this critical issue by developing and evaluating optimal investment strategies tailored to help diverse age groups achieve their homeownership goals within 5, 10, and 15-year horizons.

\subsection{Objective}
The primary objective of this study is to identify, analyze, and optimize investment strategies that can effectively assist first-time homebuyers in saving for their down payments. By leveraging advanced financial theories and empirical methodologies, this research aims to provide actionable insights that balance risk and return, offering practical solutions for prospective homeowners.

\subsection{Research Question}
The central research question guiding this investigation is: What are the most effective investment strategies for different age groups to accumulate housing down payments over periods of 5, 10, and 15 years? This question will be explored through the lens of financial optimization models and empirical data analysis.

\subsection{Motivation}
The motivation for this research stems from the pressing need to address the challenges posed by rising housing costs and economic instability. As homeownership becomes increasingly out of reach for many, particularly younger individuals, it is imperative to develop strategies that can mitigate these barriers. By providing evidence-based investment strategies, this study aims to empower individuals with the tools needed to navigate the complexities of financial planning for homeownership.

\subsection{Institutional Information}
The U.S. housing market is characterized by fluctuating prices, varying interest rates, and different lending standards. First-time homebuyers, who typically have lower income and savings, face additional challenges such as high debt-to-income ratios and stringent mortgage requirements. This study focuses on understanding how these institutional factors influence investment strategies for down payment savings.

\subsection{Scope and Significance}
This study focuses on first-time homebuyers within the United States, using data spanning from 2014 to 2023. The findings of this research are significant as they provide a blueprint for financial advisors and policymakers to design targeted savings programs, ultimately promoting economic stability and individual financial security.
