\appendix
\section{Data Appendix}

\subsection{Summary of Data Sources}
The financial data utilized in this study were obtained from Yahoo Finance, which provides comprehensive information on a range of securities including stocks, mutual funds, and ETFs.

\subsection{Data Cleaning and Processing Details}
Detailed steps taken to clean and process the data include:
\begin{itemize}
    \item Adjusting for corporate actions like stock splits and dividends to maintain consistency in price data.
    \item Interpolating missing values to handle gaps in the dataset.
    \item Detecting and handling outliers to prevent skewed results.
\end{itemize}

\subsection{Python Scripts for Data Processing}
Several Python scripts were developed to automate data collection and processing:
\begin{itemize}
    \item \texttt{yfinance\_data.py}: Collects and processes financial data from Yahoo Finance.
    \item \texttt{hindsight\_data.py}: Handles historical financial data for hindsight analysis.
    \item \texttt{init\_filtering.py}: Filters the initial dataset to remove anomalies and irrelevant data points.
\end{itemize}

\subsection{Variable Definitions}
The key variables used in the analysis are defined as follows:
\begin{itemize}
    \item \textbf{Open}: The price at the beginning of the trading day.
    \item \textbf{High}: The highest price during the trading day.
    \item \textbf{Low}: The lowest price during the trading day.
    \item \textbf{Close}: The price at the end of the trading day.
    \item \textbf{Adj Close}: The closing price adjusted for dividends, stock splits, etc.
    \item \textbf{Volume}: The number of shares traded during the trading day.
    \item \textbf{Type}: The type of security (e.g., stock, ETF).
    \item \textbf{Ticker}: The unique symbol assigned to each security for trading purposes.
    \item \textbf{Beta}: A measure of a security's volatility in relation to the overall market. A beta greater than 1 indicates that the security is more volatile than the market, while a beta less than 1 indicates that it is less volatile.
    \item \textbf{CAPM Predicted Return}: The expected return of a security as predicted by the Capital Asset Pricing Model, which takes into account the risk-free rate, the security's beta, and the expected market return.
    \item \textbf{Sharpe Ratio}: A measure of risk-adjusted return, calculated by subtracting the risk-free rate from the security's return and dividing by the standard deviation of the security's return. A higher Sharpe Ratio indicates better risk-adjusted performance.
    \item \textbf{Actual Returns}: The realized return on a security over a specified period, including price appreciation and dividends.
    \item \textbf{Composite Score}: A combined score that integrates various metrics such as Beta, CAPM Predicted Return, Actual Returns, and Sharpe Ratio to evaluate the overall attractiveness of a security. The composite score is used to rank securities.
    \item \textbf{Rank}: The position of a security in the list based on its composite score, with a lower rank indicating a more attractive investment.
\end{itemize}




\newpage
