\section{Conclusions}
\subsection{Discussion}
The findings from this research have important implications for policy and practice. Our analysis indicates that tailored investment strategies can significantly enhance the ability of first-time homebuyers to accumulate down payments. Policymakers should consider initiatives that promote financial literacy and provide access to diversified investment options. For first-time homebuyers, adopting these optimized strategies can lead to more efficient savings and faster paths to homeownership.

\subsection{Policy Implications}
\begin{enumerate}
    \item \textbf{Financial Education}: Enhance financial literacy programs to educate potential homebuyers on effective investment strategies.
    \item \textbf{Access to Investment Tools}: Provide easier access to diversified investment tools and platforms for first-time homebuyers.
\end{enumerate}

\subsection{Practical Recommendations}
\begin{enumerate}
    \item \textbf{Early Planning}: Start saving and investing early to take advantage of compounding returns.
    \item \textbf{Diversification}: Diversify investments to manage risk and optimize returns.
    \item \textbf{Regular Review}: Regularly review and adjust the investment portfolio to align with changing market conditions and personal financial goals.
\end{enumerate}

\subsection{Future Research Directions}
\begin{enumerate}
    \item \textbf{Macroeconomic Impact}: Investigate how macroeconomic factors influence the performance of optimal investment strategies.
    \item \textbf{Alternative Investments}: Explore the potential of alternative investment vehicles for down payment accumulation.
    \item \textbf{Behavioral Finance}: Study the impact of behavioral biases on investment decisions of first-time homebuyers.
\end{enumerate}

\subsection{Conclusion}
This study provides a comprehensive analysis of optimal investment strategies for accumulating housing down payments. Our findings demonstrate the importance of tailored investment strategies for different age groups, leveraging financial theories like CAPM and MPT. Future research should explore the impact of macroeconomic variables on investment strategies and extend the analysis to include alternative investment options such as real estate investment trusts (REITs) and crowdfunding platforms.
